More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-05-16 2016-Weak-FH-Bisim/WeakBisim.tex
Weak OT!

The semantics of open pNets will be defined  as an open automaton. An open
automaton is an automaton where each transition composes transitions of several LTSs with
action of some holes, the transition occurs if some predicates hold, and can involve a 
set of state modifications.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]
	\label{def:OpenTransitions}
	An \emph{open transition} over a
	set $J$ of holes with sorts $\Sort_j^{j\in J}$ and a set of states $\mathcal{S}$ is 
	a structure of the form:	
	\begin{mathpar}
	\openrule
	{	\beta_j^{j\in J}, \Pred, \Post}
	{s \OTarrow {\alpha}s'}
	\end{mathpar}
	Where $s, s'\in\mathcal{S}$ and $\beta_j$
        is a transition of the hole $j$, with $\beta_j\in\Sort_j$. $\alpha$ is an action 
        label denoting the resulting action
        of this open transition. \Pred\ is a predicate 
	over the different variables of the
	terms, labels, and states $\beta_j$, $s$, $\alpha$. \Post\ is a set of 
	equations 
	that 
	hold \emph{after the open transition}, they are represented as a substitution of the 
	form $\subst{x_k\gets e_k}^{k\in K}$ 
	where $x_k$ are variables of $s'$, and $e_k$ are expressions over the other 
	variables of the open transition. Open transitions are identified modulo logical equivalence on their predicate.
\end{definition}

@@

@@

\begin{definition}[Weak open transitions]
  Let $A = <\overline{\LTS},J,\mathcal{S},s_0,\mathcal{T}>$ be an open automaton.
  We define $\mathcal{T^*}$ the \emph{weak open transition relation}
  with respect to a set of invisible actions $\InvAct$ as:

 \begin{mathpar}
 \openrule
         {
           \beta_j^{j\in J_1},\Pred,\Post}
         {s \OTWeakarrow {\alpha} s'}
         \in \mathcal{T}^*
 \end{mathpar}

 iff there exists a sequence of open transitions
         $OT_x^{x\in X} \subseteq \mathcal{T}$ such that:

 \TODO{Pas si simple !!!!!!!!!!!!!!!!!!!}

@@

>>>>

The semantics of open pNets will be defined  as an open automaton. An open
automaton is an automaton where each transition composes transitions of several LTSs with
action of some holes, the transition occurs if some predicates hold, and can involve a 
set of state modifications.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]
	\label{def:OpenTransitions}
	An \emph{open transition} over a
	set $J$ of holes with sorts $\Sort_j^{j\in J}$ and a set of states $\mathcal{S}$ is 
	a structure of the form:	
	\begin{mathpar}
	\openrule
	{	\beta_j^{j\in J}, \Pred, \Post}
	{s \OTarrow {\alpha}s'}
	\end{mathpar}
	Where $s, s'\in\mathcal{S}$ and $\beta_j$
        is a transition of the hole $j$, with $\beta_j\in\Sort_j$. $\alpha$ is an action 
        label denoting the resulting action
        of this open transition. \Pred\ is a predicate 
	over the different variables of the
	terms, labels, and states $\beta_j$, $s$, $\alpha$. \Post\ is a set of 
	equations 
	that 
	hold \emph{after the open transition}, they are represented as a substitution of the 
	form $({x_k\gets e_k})^{k\in K}$ 
	where $x_k$ are variables of $s'$, and $e_k$ are expressions over the other 
	variables of the open transition. Open transitions are identified modulo logical equivalence on their predicate.
\end{definition}

@@

\TODO{Id(s) is the identity function on variables of state s}
\begin{definition}[Non-observability of silent actions]
An open automaton $A = <J,\mathcal{S},s_0,\mathcal{T}>$ \emph{cannot observe silent actions} if and only if for all $j$ in $J$ we have
\[ \openrule
         {
           (j\mapsto\tau),\symb{True},\symb{Id}(s)}
         {s \OTarrow {\tau} s}
         \in \mathcal{T}
\]
\end{definition}

@@

We let $\gamma$ range over lists of action terms and use $\dotcup$ as the union that appends lists of action terms \TODO{write this properly}. $[a]$ is a list with a single element.

We define $\vis{\overline\beta}$ as the mapping $\overline\beta$  without  invisible actions but where each element is now a list (if length 1).\\ $\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}$ s.t. $I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}$.

\begin{definition}[Weak open transitions]
  Let $A = <J,\mathcal{S},s_0,\mathcal{T}>$ be an open automaton. We derive the  weak invisible transition $\OTWeakarrow {\tau}$ from $\mathcal{T}$ as follows:
\begin{mathpar}
 \openrule
         {
           \emptyset,\symb{True},Id(s)}
         {s \OTWeakarrow {\tau} s}
 \end{mathpar}
and
\begin{mathpar}
\inferrule{
 \openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\tau} s'}
\\
 \openrule
         {
           \overline{\gamma},\Pred',({x_k\gets e_k})^{k\in K}   }
         {s' \OTWeakarrow {\tau} s''}
}
{ \openrule
         {
           \vis{\overline{\beta}}\dotcup\overline{\gamma},\Pred\land\Pred'\subst{\Post},
				({x_k\gets (e_k\subst \Post)})^{k\in K} } 
         {s \OTWeakarrow {\tau} s''}
}
 \end{mathpar}

And the general weak open transition $\OTWeakarrow {\alpha}$ as follows:
\begin{mathpar}
\inferrule{\openrule
         {
           \overline{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} 
\\
\openrule
         {
           \overline{\beta},\Pred_2,\Post_2  }
         {s_1 \OTarrow {\alpha} s_2} 
\\
\openrule
         {
           \overline{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
         {s_2 \OTWeakarrow {\tau} s'} 
\\
\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
}
{
\openrule
         {
           \overline{\gamma_1}\dotcup \vis{\overline{\beta}}\dotcup\overline{\gamma_3},
		\Pred,
				({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K} } 
         {s \OTWeakarrow {\alpha} s'}
}
\end{mathpar}

@@

\subsection{Non-observability and open pNets}
\begin{definition}[Non-observability of silent actions]~\\
A pNet $\mylangle \pNet_i^{i\in I} , \Sort_j^{j\in J}, \overline{\symb{SV}}\myrangle$
 \emph{cannot observe silent actions} if it verifies:\\ $\forall i\in I\uplus J.\, \SV{(i\mapsto \tau)}{\tau}{\symb{True}}\in \overline{\symb{SV}}$ and $\forall i,j\in I\uplus J.\,i\neq j \Rightarrow \alpha_i\neq\tau$
\end{definition}

\begin{property}[pNets that cannot observe silent actions]
The open semantics of a pNets that cannot observe silent actions is an open automaton that  cannot observe silent actions.
\end{property}
